### 2019-05-21 Papers/Notes_TeX/pages/paper_notes.tex
Changes; - More paper notes addded

\begin{itemize}
    \item X
\end{itemize}

@@

\subsection{Findings}
\begin{itemize}
    \item Overall recommendation is to replace \textbf{hexadecimal} with \textbf{sentence} based encoding
    \item Findings show that \textbf{hexadecimal} and \textbf{Base32} perform worse than the other alternatives in realistic threat models. With over \textbf{10\%} of users failing to detect attacks with these schemes.
\end{itemize}

>>>>

\begin{itemize}
    \item Alphanumerical
    \item Numerical
    \item Words
    \item Sentences
\end{itemize}

@@

\subsection{Findings}
\begin{itemize}
    \item Overall recommendation is to replace \textbf{hexadecimal} with \textbf{sentence} based encoding
    \item Findings show that \textbf{hexadecimal} and \textbf{Base32} perform worse than the other alternatives in realistic threat models. With over \textbf{10\%} of users failing to detect attacks with these schemes.
    \item According to their study, \textbf{words} and \textbf{sentences} we some of the best methods for avoiding attack
    \item Words has the second highest usability ratings second to only sentences
\end{itemize}

\section{Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols}

Paper looks into the positives of secondary channels used to authenticate device pairing. Such as device fingerprint comparison.

"People are the weakest link in the security chain" [26]

Mentions a normal channel as a "Dolev-Yao" channel [5]. This is where an attacker can overhead, delete and modify messages.

\subsection{Findings}
\begin{itemize}
    \item Showed for \textbf{usability} methods ranked:
    \begin{itemize}
        \item Comparing-confirm
        \item Typing strings
        \item Comparing-select
        \item Barcode
    \end{itemize}

    \item Showed for \textbf{combined security} and \textbf{usability} methods ranked:
    \begin{itemize}
        \item Typing strings
        \item Barcodes
        \item Comparing-confirm
        \item Comparing-select
    \end{itemize}
\end{itemize}
